### 2022-04-26 ms/ms.rmd
Add rlang

##################################
# Loading packages & Functions
##################################
    pacman::p_load(tidyverse, kableExtra, gridExtra, magrittr, Hmisc, googlesheets4, metafor, stringr, formatR, rmarkdown, kableExtra, flextable, raster, rasterVis, rnoaa, sp, ggmap, patchwork, ggpubr, RColorBrewer, sf, ggtree, ape, phytools, viridis, ncdf4.helpers, ncdf4, PCICt, readr, chron, tmap, rgdal, MCMCglmm, brms, latex2exp)

>>>>

##################################
# Loading packages & Functions
##################################
    pacman::p_load(tidyverse, kableExtra, gridExtra, magrittr, Hmisc, googlesheets4, metafor, stringr, formatR, rmarkdown, kableExtra, flextable, raster, rasterVis, rnoaa, sp, ggmap, patchwork, ggpubr, RColorBrewer, sf, ggtree, ape, phytools, viridis, ncdf4.helpers, ncdf4, PCICt, readr, chron, tmap, rgdal, MCMCglmm, brms, latex2exp, rlang)
